Staged Abstract Interpreters

### 2019-09-11 paper/40_absinterp.tex
misc

It is important that the abstract stores now map addresses to sets of abstract
values, indicating that an address may point to an over-approximated set of
runtime values.  This can be justified by the approximation nature and
nondeterminism during the analysis.  For example, when analyzing a
conditional expression, we may not have enough information to decide which
branch will be taken, thus a sound treatment is to explore the both branches.
Also, at some later point, we need to compute the join of two path.  Another
nondeterminism comes from function applications, for instance, @f(a)@, the
possible $\lambda$ terms of @f@ are computed approximately.  As the
result, we need to store all the possible callees, as well as we will
retrieve a set of closures when dereferencing an address.

>>>>

It is important that the abstract stores now map addresses to sets of abstract
values, indicating that an address may point to an over-approximated set of
runtime values.  This can be justified by the approximation nature and
nondeterminism during the analysis.  For example, when analyzing a
conditional expression, we may not have enough information to decide which
branch will be taken, thus a sound treatment is to explore both of the branches.
Also, at some later point, we need to compute the join of two path.  Another
nondeterminism comes from function applications, for instance, @f(a)@, the
possible $\lambda$ terms of @f@ are computed approximately.  As the
result, we need to store all the possible callees, as well as we will
retrieve a set of closures when dereferencing an address.
